TacticToe: Learning to Prove with Tactics

### 2018-03-23 tactictoe_jv.tex
More formatting edits

The first similarity measure $sim_1$ sums the weight of all shared
features to compute the total score.
In a second similarity measure $sim_2$, we additionally take
the total number of features into account, to reduce the seemingly unfair
advantage of big
feature sets in the first scoring function.
\[sim_1 (o_1, o_2) = {\sum\nolimits_{\,f \in f_0 \cap
f_1}{\text{tfidf}(f)^{6}}}\]
\[sim_2 (o_1, o_2) = \frac{{\sum\nolimits_{\,f \in f_0 \cap
f_1}{\text{tfidf}(f)^{6}}}}
{ln (e + \mathit{card} f_0 + \mathit{card} f_1)}\]

In our setting, making predictions for an object $o$ consists of sorting a set
of objects by their similarity to $o$. We use $sim_1$ for tactics and theorems
and $sim_2$ for lists of goals. The reason why $sim_1$ is used for
predicting tactics is that tactics effective on a large goal $g$ are often also
suitable for a goal made of sub-formulas of $g$. The same monotonicity
heuristic can justify the use of $sim_1$ for theorems. Indeed, in practice a
large theorem is often a conjunction of theorems from the same domain.
And if a conjunction contains a formula related to a problem, then the other
conjuncts from the same domain may also help to solve it.

@@

\begin{definition} (Coverage)\\
Let $\mathfrak{T}$ be the database of goal-tactic pairs. We define the
coverage $\textit{\mbox{Coverage}}(t)$ of a tactic $t$ by the number of times
this tactic
appears in
$\mathfrak{T}$. Expressing this in a formula, we get:
\[\textit{\mbox{Coverage}}(t) =_{\mathrm{def}} card\ \lbrace g\ |\ (t,g) \in
  \mathfrak{T} \rbrace \]
Intuitively, this notion estimates how general a tactic is by counting the
number of different goals it is useful for.
\end{definition}

>>>>

The first similarity measure $\mathit{sim}_1$ sums the weight of all shared
features to compute the total score.
In a second similarity measure $\mathit{sim}_2$, we additionally take
the total number of features into account, to reduce the seemingly unfair
advantage of big
feature sets in the first scoring function.
\[\mathit{sim}_1 (o_1, o_2) = {\sum\nolimits_{\,f \in f_0 \cap
f_1}{\mathrm{tf\_idf}(f)^{6}}}\]
\[\mathit{sim}_2 (o_1, o_2) = \frac{{\sum\nolimits_{\,f \in f_0 \cap
f_1}{\mathrm{tf\_idf}(f)^{6}}}}
{ln (e + |f_0| + |f_1|)}\]

In our setting, making predictions for an object $o$ consists of sorting a set
of objects by their similarity to $o$. We use $\mathit{sim}_1$ for tactics and theorems
and $\mathit{sim}_2$ for lists of goals. The reason why $\mathit{sim}_1$ is used for
predicting tactics is that tactics effective on a large goal $g$ are often also
suitable for a goal made of sub-formulas of $g$. The same monotonicity
heuristic can justify the use of $\mathit{sim}_1$ for theorems. Indeed, in practice a
large theorem is often a conjunction of theorems from the same domain.
And if a conjunction contains a formula related to a problem, then the other
conjuncts from the same domain may also help to solve it.

@@

\begin{definition} (Coverage)\\
Let $\mathfrak{T}$ be the database of goal-tactic pairs. We define the
coverage $\textit{\mbox{Coverage}}(t)$ of a tactic $t$ by the number of times
this tactic
appears in
$\mathfrak{T}$. Expressing this in a formula, we get:
\[\textit{\mbox{Coverage}}(t) =_{\mathrm{def}} |\lbrace g\ |\ (t,g) \in
  \mathfrak{T} \rbrace| \]
Intuitively, this notion estimates how general a tactic is by counting the
number of different goals it is useful for.
\end{definition}
